Synpotic Soil Characterization

### 2025-08-12 3-reports/manuscript_figures.Rmd
fix figure sizes

```{r}
source("2-code/0-packages.R")
library(ggbiplot)

@@

gg_pca_wle = 
  ggbiplot(pca_overall_wle$pca_int, obs.scale = 1, var.scale = 1, varname.size = 5,
           groups = as.character(pca_overall_wle$grp$transect), 
           ellipse = TRUE, circle = FALSE, var.axes = TRUE, alpha = 1) +
  geom_point(size=5,stroke=1, alpha = 1,
             aes(shape = pca_overall_wle$grp$site,
                 fill = groups), 
             stroke = 1)+ 
  scale_color_manual(breaks = c("upland", "transition", "wte", "wetland"), 
                     values = pal_transect)+
  scale_fill_manual(breaks = c("upland", "transition", "wte", "wetland"), 
                    values = pal_transect)+
  scale_shape_manual(values = c(21, 24, 22))+
  xlim(-3, 5)+
  ylim(-2.5, 3.5)+
  labs(shape="", fill = "", color = "")+ 
  theme_kp()+
  theme(legend.position = "top", legend.box = "vertical")+
  guides(fill = guide_legend(override.aes = list(alpha=1, shape = 21, size = 3)))+
  NULL

gg_pca_cb = 
  ggbiplot(pca_overall_cb$pca_int, obs.scale = 1, var.scale = 1, varname.size = 5,
           groups = as.character(pca_overall_cb$grp$transect), 
           ellipse = TRUE, circle = FALSE, var.axes = TRUE, alpha = 0) +
  geom_point(size=5,stroke=1, alpha = 1,
             aes(shape = pca_overall_cb$grp$site,
                 fill = groups), 
             stroke = 1)+ 
  scale_color_manual(breaks = c("upland", "transition", "wte", "wetland"), 
                     values = pal_transect)+
  scale_fill_manual(breaks = c("upland", "transition", "wte", "wetland"), 
                    values = pal_transect)+
  scale_shape_manual(values = c(21, 24, 22))+
  xlim(-5, 3)+
  ylim(-2.5, 3.5)+
  labs(shape="", fill = "", color = "")+ 
  theme_kp()+
  theme(legend.position = "top", legend.box = "vertical")+
  guides(fill = guide_legend(override.aes = list(alpha=1, shape = 21, size = 3)))+
  NULL

@@

data_scaled_NEW2 %>% 
  ggplot(aes(x = transect, y = value_scaled, group = site, color = site))+
  geom_line(linewidth = 1) + geom_point(size = 4, aes(shape = site, fill = site), color = "black")+
#  facet_wrap( ~ name)+
  facet_nested_wrap(~ name + region, ncol = 4,
                    nest_line = element_line(colour = "grey"))+ 
  scale_color_manual(breaks = c("CRC", "PTR", "OWC",
                                "GCW", "MSM", "GWI"),
                     values = c("#d73027", "#fc8d59", "#fdbb84", 
                                "#74a9cf", "#2b8cbe", "#045a8d"))+
    scale_fill_manual(breaks = c("CRC", "PTR", "OWC",
                                "GCW", "MSM", "GWI"),
                     values = c("#d73027", "#fc8d59", "#fdbb84", 
                                "#74a9cf", "#2b8cbe", "#045a8d"))+
  scale_shape_manual(breaks = c("CRC", "PTR", "OWC",
                                "GCW", "MSM", "GWI"),
                     values = c(21, 23, 24, 21, 23, 24))+
  scale_x_discrete(labels = c("U", "T" , "W" ))+
  labs(x = "Transect", y = "Normalized concentration")+
  theme_kp()+
  theme(axis.text.y = element_blank(),
        panel.grid = element_blank())

@@

```{r v2-scaled_gg2_gwi, fig.height = 8, fig.width = 8, eval=FALSE}
data_scaled_NEW %>% 
  filter(site == "GWI") %>% 
  ggplot(aes(x = transect, y = value_scaled, group = site, color = site))+
  geom_line(linewidth = 1) + geom_point(size = 2)+
  facet_wrap( ~ name )+
  scale_color_manual(breaks = c("CRC", "PTR", "OWC",
                                "GCW", "MSM", "GWI"),
                     values = c("#d73027", "#fc8d59", "#fdbb84", 
                                "#74a9cf", "#2b8cbe", "#045a8d"))+
  scale_x_discrete(labels = c("U", "T" , "W" ))+
  labs(x = "Transect", y = "Normalized concentration")+
  theme(axis.text.y = element_blank(),
        panel.grid = element_blank())

>>>>

```{r}
source("2-code/0-packages.R")
library(ggbiplot)
library(targets)

@@

gg_pca_wle = 
  ggbiplot(pca_overall_wle$pca_int, obs.scale = 1, var.scale = 1, varname.size = 5,
           groups = as.character(pca_overall_wle$grp$transect), 
           ellipse = TRUE, circle = FALSE, var.axes = TRUE, alpha = 1) +
  geom_point(size=5,stroke=1, alpha = 1,
             aes(shape = pca_overall_wle$grp$site,
                 fill = groups), 
             stroke = 1)+ 
  scale_color_manual(breaks = c("upland", "transition", "wte", "wetland"), 
                     values = pal_transect)+
  scale_fill_manual(breaks = c("upland", "transition", "wte", "wetland"), 
                    values = pal_transect)+
  scale_shape_manual(values = c(21, 24, 22))+
  xlim(-3, 5)+
  ylim(-2.5, 3.5)+
  labs(shape="", fill = "", color = "")+ 
  theme_kp()+
  theme(legend.position = "top", legend.box = "vertical",
        axis.text = element_text(size = 16, color = "black"),
        axis.title = element_text(size = 16, face = "bold", color = "black"),
  )+
  guides(fill = guide_legend(override.aes = list(alpha=1, shape = 21, size = 3)))+
  NULL

gg_pca_cb = 
  ggbiplot(pca_overall_cb$pca_int, obs.scale = 1, var.scale = 1, varname.size = 5,
           groups = as.character(pca_overall_cb$grp$transect), 
           ellipse = TRUE, circle = FALSE, var.axes = TRUE, alpha = 0) +
  geom_point(size=5,stroke=1, alpha = 1,
             aes(shape = pca_overall_cb$grp$site,
                 fill = groups), 
             stroke = 1)+ 
  scale_color_manual(breaks = c("upland", "transition", "wte", "wetland"), 
                     values = pal_transect)+
  scale_fill_manual(breaks = c("upland", "transition", "wte", "wetland"), 
                    values = pal_transect)+
  scale_shape_manual(values = c(21, 24, 22))+
  xlim(-5, 3)+
  ylim(-2.5, 3.5)+
  labs(shape="", fill = "", color = "")+ 
  theme_kp()+
  theme(legend.position = "top", legend.box = "vertical",
        axis.text = element_text(size = 16, color = "black"),
        axis.title = element_text(size = 16, face = "bold", color = "black"),
  )+
  guides(fill = guide_legend(override.aes = list(alpha=1, shape = 21, size = 3)))+
  NULL

@@

data_scaled_NEW2 %>% 
  ggplot(aes(x = transect, y = value_scaled, group = site, color = site))+
  geom_line(linewidth = 1) + geom_point(size = 4, aes(shape = site, fill = site), color = "black")+
#  facet_wrap( ~ name)+
  facet_nested_wrap(~ name + region, ncol = 4,
                    nest_line = element_line(colour = "grey"))+ 
  scale_color_manual(breaks = c("CRC", "PTR", "OWC",
                                "GCW", "MSM", "GWI"),
                     values = c("#d73027", "#fc8d59", "#fdbb84", 
                                "#74a9cf", "#2b8cbe", "#045a8d"))+
    scale_fill_manual(breaks = c("CRC", "PTR", "OWC",
                                "GCW", "MSM", "GWI"),
                     values = c("#d73027", "#fc8d59", "#fdbb84", 
                                "#74a9cf", "#2b8cbe", "#045a8d"))+
  scale_shape_manual(breaks = c("CRC", "PTR", "OWC",
                                "GCW", "MSM", "GWI"),
                     values = c(21, 23, 24, 21, 23, 24))+
  scale_x_discrete(labels = c("U", "T" , "W" ))+
  scale_y_continuous(breaks = c(0, 0.5, 1), labels = c(0, "" , 1))+
  labs(x = "Transect", y = "Scaled concentration
       ")+
  theme_kp()+
  theme(#axis.text.y = element_blank(),
        panel.grid = element_blank()
        )

@@

```{r v2-scaled_gg2_gwi, fig.height = 8, fig.width = 8, eval=FALSE}
data_scaled_NEW %>% 
  filter(site == "GWI") %>% 
  ggplot(aes(x = transect, y = value_scaled, group = site, color = site))+
  geom_line(linewidth = 1) + geom_point(size = 2)+
  facet_wrap( ~ name )+
  scale_color_manual(breaks = c("CRC", "PTR", "OWC",
                                "GCW", "MSM", "GWI"),
                     values = c("#d73027", "#fc8d59", "#fdbb84", 
                                "#74a9cf", "#2b8cbe", "#045a8d"))+
  scale_x_discrete(labels = c("U", "T" , "W" ))+
  scale_y_continuous(breaks = c(0, 0.5, 1), labels = c(0, "" , 1))+
  labs(x = "Transect", y = "Scaled concentration
       ")+
  theme(axis.text.y = element_blank(),
        panel.grid = element_blank())
